Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-20 longSC.tex
new figures

\begin{figure*}[h]
            \begin{center}
%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3-5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations. The SC(4,2) and SC(3,2) are downscaled by 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

>>>>

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
%			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations. The SC(4,2) and SC(3,2) are downscaled by 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}
